---
Y---
title: "2T2C"
author: "Ted Aplin"
format: html
editor: visual
---

# Initialisation

## RENV (Y*ou don't need to run this every time)*

```{r}
renv::restore()
renv::status()
```

## Loading packages

```{r}
#| label: Packages
# loading packages
library(tidyverse)
library(here)

# loading personal functions
source(here("Functions", "Functions for 2T2C.R"))
```

# Data preparation

## loading

Place your data into the "Input" folder then enter in the following details here, a demo from the test data-set is here by default. **If there is any information you would not like to enter, write FALSE in block capitals with no quotation marks.**

-   File name including extension (.csv)

-   The time interval between frames in Seconds

-   The number of the channel that contains the calcium data

-   The number of the channel that contains the background data

-   the names you would like to give to your sensors

-   the names you would like to give your ROIs

```{r}
#| label: Data loading and Wrangling
# Input file name in the format "file name.csv" MUST BE ENTERED
FileName <- "Test Results.csv"

# Input time interval as a number with no quotation marks
TimeInterval <- 3

## Inputting Channel information
# Input Calcium channel number with no quotation marks
CalciumChannel <- 5

# Input Background channel number with no quotation marks
BackgroundChannel <- 2

# Input sensor names in the form c("name for sensor 1", "name for sensor 2", ...)
SensorNames <- c("Sensor 1", "Sensor 2")

## Inputting ROI information
# Input background ROI number with no quotation marks
BackgroundROI <- 7

# Input ROI names in the form c("name for ROI 1", "name for ROI 2", ...)
ROINames <- c("ROI 1", "ROI 2")



##################################################################
## functions for loading and Wrangling Data, do not touch!
# loading your dataset
if (endsWith(FileName, ".csv") != TRUE){
  cat('You must enter a filename in the form "file name.csv"', "\n")
} else{
  Input <- read.csv(here("Input", FileName))
  # creating Dataset from your Inputted information and saving it to Output\Data
  Data <- DataWrangling(FileName, Input, TimeInterval, SensorNames, ROINames)
}
```

## calculations

# Visualisation

## All

## Individual cells

```{r}
cat("ERROR: Something went wrong\n")
cat("This message is not an error.\n")
```
