---
---
title: "2T2C"
author: "Ted Aplin"
format: html
editor: visual
---

# Initialisation

Make sure you have run Initialisation.R before using this file for the first time, if any packages fail to load, then run it again.

```{r}
#| label: Packages
# loading packages
library(tidyverse)
library(here)
library(png)
library(svglite)
library(pals)
# library(doParallel)
# closeAllConnections()
# registerDoParallel(cores=16)

# loading personal functions
source(here("Functions", "Functions for 2T2C.R"))
```

# Data preparation

## loading

Place your data into the "Input" folder then enter in the following details here, a demo from the test data-set is here by default. **If there is any information you would not like to enter, write 0.**

-   File name including extension (.csv)

-   The time interval between frames in Seconds

-   The number of the channel that contains the calcium data

-   The number of the channel that contains the background data

-   the names you would like to give to your sensors

-   the names you would like to give your ROIs

```{r}
#| label: Data loading and manual data input
# Input file name in the format "file name.csv" MUST BE ENTERED
InputFileName <- "MAX_WT 8 15,07,25_1.csv"

# Input time interval as a number with no quotation marks
TimeInterval <- 3

# Input sensor names in the form c("name for sensor 1", "name for sensor 2", ...)
SensorNames <- c("GFP", "RFP")

# Input ROI names in the form c("name for ROI 1", "name for ROI 2", ...)
ROINames <- c("Airpore Old 1", "Airpore Old 2", "Airpore Old 3", "Airpore Medium 1", "Airpore Medium 2", "Background", "Background")



##################################################################
## functions for loading and Extending Data, do not touch!
# creating Dataset from your Inputted information and saving it to Output/Data
  OGData <- DataExtending(InputFileName, TimeInterval, SensorNames, ROINames)
```

## Data Wrangling

This changes the Data into a format which is more useful for analysis. As well as calculating the ratio *(if the calcium and background channel number have been added correctly)* and a normalised this ratio using the background ROI *(if a background ROI has been correctly identified)*.

```{r}
#| label: Wrangling
## Inputting Channel information
# Input Calcium channel number with no quotation marks
CalciumChannel <- 1

# Input Background channel number with no quotation marks
BackgroundChannel <- 2

## Inputting ROI information
# Input background ROI number with no quotation marks, if you want to add multiple do it in the form c(1, 2, ...)
BackgroundROI <- c(6,7)


##################################################################
## functions for Wrangling Data, do not touch!
# Creating the new Dataset
Data <- DataWrangling(OGData, CalciumChannel, BackgroundChannel, BackgroundROI, InputFileName)
```

# Octave integration

This is for use with the previously made code for Octave. To use, please install Octave from this link and follow the Octave section of the README file:

Octave for Mac: <https://octave-app.org/Developer-Downloads.html> Octave for Windows: <https://www.gnu.org/software/octave/download.html#ms-windows>

```{r}
#| label: Creation of Octave File
OctaveFile(Data, InputFileName)
```

# Visualisation

set Ylimit to 0 if you want it to be set automatically based on the largest value in your dataset.

```{r}
GraphName <- "WT 1"

# enter the maximum Y value for the graph, if you want this to be set automatically put 0
YLimit <- 0

# enter the resoltuion of the graph in the form c(X, y, DPI)
Resolution <- c(1200,500,200)



##################################################################
## functions for creating graphs, do not touch!
# Creating a graph of all data
YLimitAuto <- LineGraph(Data, InputFileName, GraphName, YLimit, Resolution)

# creating indivual graphs
for(i in 1:as.integer(max(Data$ROI))){
  GraphData <- filter(Data, ROI == i)
  OutputName <- paste0(GraphName, " - ", GraphData$ROIName[1])
  LineGraph(GraphData, InputFileName, OutputName, 
            YLimitAuto, Resolution,  i)
}
```

# Comparing background signals

if Permission is Denied, then make sure that you don't have the .csv file open in any programs.

```{r}
#| label: setting background file name
BackgroundFileName <- "Background.csv"
```

```{r}
#| label: adding Background Data
BackgroundTable(Data, Sample,  BackgroundFileName, InputFileName)
```

## T test

```{r}
#| label: Background T Test
TT1 <- read.csv(here("Output", "Data", "WTBackground.csv"))
TT2 <- read.csv(here("Output", "Data", "CNGCBackground.csv"))
t.test(TT1, TT2)
```
